visdat: Visualising whole data frames

### 2017-01-08 paper/paper.Rmd
first submission of paper.md

---
title: 'visdat: Visualising whole data frames'
tags:
  - visualisation
  - R
  - exporatory data analysis
authors:
 - name: Nicholas Tierney
   orcid: 0000-0003-1460-8722
   affiliation: 1
affiliations:
 - name: Queensland University of Technology
   index: 1
date: 09 January 2017
# bibliography: paper.bib
output: 
  html_document: 
    keep_md: yes
---

@@

As described by Hadley Wickham, there are 6 phases of data science:

@@

Another alterantive is `dplyr::glimpse`

@@

And it might be a bit unclear where to go from there. Do you plot the data? Why does my plot look wierd? What are these other strange features in the data? The `visdat` package provides visualisations of an entire dataframe at once. Initially inspired by [`csv-fingerprint`](https://github.com/setosa/csv-fingerprint), `visdat` provides tools to create heatmap-like visualisations of an entire dataframe. `visdat` [@Tierney2017] is an R [@Rcore] package provides 2 main functions `vis_dat` and `vis_miss`.

@@

These functions provide useful tools to help "get a look at the data", using principled visualisation techniques. The plots are built using ggplot2 [@ggplot2], which provides a consistent and powerful framework for visualisations. Which means that users can customise and extend graphics from visdat very easily.

>>>>

---
title: 'visdat: Visualising whole data frames'
tags:
  - visualisation
  - R
  - exporatory data analysis
authors:
 - name: Nicholas Tierney
   orcid: 0000-0003-1460-8722
   affiliation: 1
affiliations:
 - name: Queensland University of Technology
   index: 1
date: 09 January 2017
bibliography: paper.bib
output: 
  html_document: 
    keep_md: yes
---

@@

As described by Hadley Wickham [@wickham2016], there are 6 phases of data science:

@@

Another alterantive is `glimpse`, from the `dplyr` package [@dplyr]

@@

And it might be a bit unclear where to go from there. Do you plot the data? Why does my plot look wierd? What are these other strange features in the data? The `visdat` package provides visualisations of an entire dataframe at once. Initially inspired by [`csv-fingerprint`](https://github.com/setosa/csv-fingerprint), `visdat` provides tools to create heatmap-like visualisations of an entire dataframe. `visdat` is an R [@Rcore] package provides 2 main functions `vis_dat` and `vis_miss`.

@@

These functions provide useful tools to help "get a look at the data", using principled visualisation techniques. The plots are built using ggplot2 [@ggplot2], which provides a consistent and powerful framework for visualisations. This means that users can customise and extend graphics from visdat very easily.
